Detecting changes in dispersion in COVID-19 incidence time series using a negative binomial model

### 2023-06-09 noise_covid_v2.Rmd
add text about V(mu) = 0

In some time windows, the Likelihood-Ratio statistic can't be computed because (TODO**: the weight matrix in the IRLS can't be calculated?).

>>>>

In some time windows, the Likelihood-Ratio statistic can't be computed due to zero variance: the variance of mu is a function of mu and dispersion, both of which are zero in a stretch of zeroes.
